---
title: "Quarto Report"
author: "Perla Colombani"
format: html
---



```{r}
1 + 1
```


```{r}
#| echo: false
if (!require("ggplot2")) install.packages("ggplot2", dependencies = TRUE) 
if (!require("tidyverse")) install.packages("tidyverse", dependencies = TRUE)
if (!require("mapdata")) install.packages("mapdata", dependencies = TRUE)

library(ggplot2)              #needs to be done each r session
library(tidyverse)            #needs to be done each r session
library(mapdata)  #needs to be done each r session

unicef_indicator_1 <- read.csv("/cloud/project/unicef_indicator_1.csv")

mapdata <- map_data("world") ##ggplot2
mapdata <- left_join(mapdata, unicef_indicator_1, by="region")
mapdata <- filter(mapdata, time_period == 2020)
map1<-ggplot(mapdata, aes( x = long, y = lat, group=group)) +
  geom_polygon(aes(fill = obs_value), color = "grey")

map2 <- map1 + scale_fill_gradient(name = "sanitation access (%)", low = "red", high =  "beige", na.value = "grey50")+
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.title.y=element_blank(),
        axis.title.x=element_blank(),
        rect = element_blank())

# Ajouter un titre au graphique
map2 <- map2 + ggtitle("Unequal access to sanitation in the world")

# Afficher le graphique avec le titre
print(map2)
```

```{r}
#| echo: false

install.packages("ggplot2") # To create the bar chart

library(ggplot2)

# Load data
my_data <- read.csv("/cloud/project/unicef_indicator_1.csv")
View(unicef_indicator_1)

# Create the bar chart
my_chart <- ggplot(my_data, aes(x = time_period, y = obs_value, fill =region)) +
  geom_bar(stat = "identity", fill = "bisque1") +  # Customize the appearance of the bars
  labs(title = "Increasing sanitation access over time", x = "Years", y = "Sanitation access") +  # Customize titles and axis labels
  theme_minimal() # Customize the overall theme of the chart

# Display the chart
print(my_chart)
